### 2022-05-24 GB_Simulation_3Species.Rmd
Improving generality, especially in plotting at the end

  #load increase temp data from Mars
  load("/net/home5/blevy/Bens_R_Projects/READ-PDB-blevy2-MFS2/Results/GB_3species_ConsPop_ConsTemp_environment.RData")

@@

nCoresToUse <- 5

@@

#save results
save.image("/net/home5/blevy/Bens_R_Projects/READ-PDB-blevy2-MFS2/Results/GB_3species_ConsPop_ConsTemp_RESULTS.RData")

>>>>

  #load increase temp data from Mars
  load("/net/home5/blevy/Bens_R_Projects/READ-PDB-blevy2-MFS2/Results/GB_3species_IncPop_IncTemp_environment.RData")

@@

nCoresToUse <- 4

@@

#save results
save.image("/net/home5/blevy/Bens_R_Projects/READ-PDB-blevy2-MFS2/Results/GB_3species_ConPop_IncTemp_RESULTS.RData")
